---
title: "WUP_09"
author: "Quintin Burnett"
date: "fall 2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt", sep="", header=TRUE)
```

### Model1: SIMS~ARM

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS~ARM")+ theme(plot.title = element_text(hjust = 0.5, size = 20))
```

This scatter plot has a positive slope going up. This shows the average amount of strength lies withing 50 and 100. What the plot describes is the relation of arm strength for the select employees.

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```

This has a high positive correlation for SIMS~ARM. The closer to 1, the results get a higher correlation. From this we can say that they are related to each other.

### Inferential Results
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

From the inferential results, we can get our equation for our line of best fit. > SIMS = 0.054563 * ARM - 4.095160.
